---
title: "session33"
author: "Dianah Okia"
date: "1/13/2020"
output:
  word_document: default
  html_document: default
---

---
#importing dataset
```{r}
library(tidyverse)
mobile2<-read_csv("https://raw.githubusercontent.com/vmandela99/Class-assignment-12th-july-2019/master/mobilemoney_data.csv")
```

##report on summary

skimr::skim(mobile2)

the data has 2509 number of rows and 28 number of columns
the pipe fxn(%>%) means "then"

```{r}
#how many account types are there
mobile2 %>% count(account_type) %>% ggplot(aes(x=account_type,y=n)) + geom_col()
```

the account types are 7
825 people have mobile money account, 669 have VSLA account,467 have SACCO account,
323 have bank account,82 have MFI account, 12 have online bank account and 131 have none

#which districts have many people?

```{r}
#which districts have many people?
mobile2 %>% count(district) %>% ggplot(aes(x=district,y=n)) + geom_col()
```

District C has the most people. It has 856 people. It is followed by district B,which has 838 people and then District A which has 815 people.
for question 1 and 2 we were focusing on the function "count". for qsn 3 onwards we introduce mutate fxn

```{r}
#what percentage of people from district A have accounts
mobile2 %>% count(district) %>% mutate(percent = n/sum(n)*100)
```
32% of pple in district A have accounts,33% in district B and 34% in district C

```{r}
#what percentage of people have SACCO accounts from district A, in the entire data?
mobile2 %>% count(district,account_type) %>% mutate(percent = n/sum(n)*100)
```

In the entire data,5.8987% of people who have SACCO account are from district A

```{r}
#What percentage of people from district A have SACCO accounts
#we introduce filter function to answer the question
mobile2 %>% filter(district == "District_A") %>% count(account_type) %>% mutate(percent = n/sum(n)*100) %>% ggplot(aes(x=account_type, y=n)) + geom_col()

```
18.15% of people in District A have SACCO  account

```{r}
#how many grades completed are there
mobile2 %>% count(highest_grade_completed) %>% ggplot(aes(x= highest_grade_completed, y= n)) +geom_col()
```
Grades completed are 16, with primary 6 being the grade completed by the highest number of people(671)

```{r}
#what is the largest weight in the survey
max(mobile2$weight)
```
The largest weight in the survey is 4812.165

```{r}
#what percentage of people ar ein university and have mobile money accounts
mobile2 %>% filter(highest_grade_completed == "university") %>% count(account_type) %>% mutate(percent = n/sum(n)*100)
```
32.39% of people in university have mobile money account
